---
title: "2 Justify Sample Size"
format: html
editor: visual
---

```{r setup}
library(tidyverse)
library(rstan)
library(patchwork)
library(tidybayes)

options(mc.cores = 8)

# set global ggplot theme
theme_set(theme_bw())

source("../functions/sim_foraging_data.R")
source("../functions/prep_data.R")
source("../functions/get_run_info.R")
```

# Simulate Data

First we will simulate data using the parameters below. These are based on the model fits from Clarke, Hunt & Hughes (2022, Comp. Bio.) to data from Clarke et al (2022, QJEP) and Tagu & Kristjansson (2021).

```{r sim_data}
######################################################
# first of all we want to generate some synthetic data
######################################################
cond_labels <- c("equal", "scarce")

# number of participants should be a multiple of 6 due to counter balancing
n_people <- 6
n_trials_per_cond <- 5

n_targ_class <- 2
n_targ_per_class <- list(c(10, 10), c(5, 15))
targ_class_weights <- list(c(1,1), c(3,2)) # compared to approx 3:1 (75%) in Tagu & Kristjansson (2021)

pA <- c(
  targ_class_weights[[1]][1]/sum(targ_class_weights[[1]]), 
  targ_class_weights[[2]][1]/sum(targ_class_weights[[2]]))

b_stick <- 1
sig_d <- 15
sig_theta <- -2

# random effect sds
phi_class_weights <- 0.05
phi_stick <- 0.5
phi_d <- 5
phi_theta <- 0.5

n_conditions <- length(n_targ_per_class)
```

```{r run_model}

# now simulate data
d <- sim_foraging_people(n_people = n_people,
                         n_conditions = n_conditions,
                         n_trials_per_cond = n_trials_per_cond,
                         n_targ_class = n_targ_class,
                         n_targ_per_class = n_targ_per_class,
                         targ_class_weights = targ_class_weights, phi_class_weights = phi_class_weights,
                         bS = b_stick, sig_d = sig_d, sig_theta = sig_theta, # fixed effects
                         phi_stick = phi_stick, phi_d = phi_d, phi_theta = phi_theta) # random effects)
# 
write_csv(d %>% mutate(x = round(x, 3), y = round(y, 3)), "../scratch/sim_data.csv")
```

Read in pre-generated data and summarise randomly generated simulation parameters

```{r summarise_sim_data}
d <- read_csv("../scratch/sim_data.csv")

d %>% group_by(person, condition) %>%
  summarise(bA = unique(bA),
    bS = unique(bS),
            sig_d = unique(sig_d),
            sig_theta = unique(sig_theta),
    .groups = "drop") -> sim_params

sim_params %>% 
  pivot_longer(-c(person, condition), names_to = "param", values_to = "value") %>%
  ggplot(aes(value, fill = as_factor(condition))) + 
  geom_histogram(alpha = 0.25, position = position_identity(), bins = 10) + 
  scale_fill_discrete("condition") + 
  facet_wrap(~param, scales="free")
```

## Summary Statistics

Compute and plot some summary run length parameters

```{r compute_run_stats, fig.height=3}
######################################################
# check summary stats
######################################################
d %>% modelr::data_grid(person, trial, condition) %>% 
  rename(pp = "person", trl = "trial", blk = "condition") -> d_trls

d_runs <- pmap_df(d_trls, get_run_info, d)

d_runs %>% group_by(person, block) %>%
  summarise(mean_max_run = mean(max_run_length),
            mean_num_run = mean(n_runs),
            .groups = "drop") %>%
  full_join(sim_params) -> d_runs

d_runs %>% select(person, block, mean_max_run, mean_num_run) %>%
  pivot_longer(-c(person, block), names_to = "run_statistic", values_to = "value") %>%
  mutate(block = as_factor(block)) %>%
  ggplot(aes(block, value, fill = run_statistic)) + 
  geom_boxplot() +
  facet_wrap(~run_statistic)
```

## Running the model

```{r set_up_data}
######################################################
# now prepare data for stan model
######################################################

d_stim <- d %>% select(person, condition, trial, id, x, y, class) %>%
  arrange(person, condition, trial, id) %>%
  filter(class > 0)

d_found <- d %>% filter(found > 0) %>% 
  arrange(person, condition, trial, found) 
```

The code below runs the model. However, to make it easier to compile this document, this is pre-computed.

```{r create_stan_list}
d_list <- prep_data_for_stan(d_found, d_stim)
saveRDS(d_list, "../scratch/sensiv_sim.d_list")
```

```{r fit_model}
d_list <- readRDS("../scratch/sensiv_sim.d_list")

######################################################
# run model
######################################################

m <- stan("../models/foraging_model1_nonml.stan", data = d_list, 
           chains = 4, iter = 1000)

saveRDS(m, "../scratch/sensiv_sim.model")
```

Here we load in the model we fit earlier

```{r}
m <- readRDS("../scratch/sensiv_sim.model")
```

## Posterior Probabilities

```{r plot_model_post, fig.height=2.8}
######################################################
# plot model
######################################################

# functions for plotting the model are in this script: 
source("../../foraging_spatial/functions/plot_model.R")    

# plot the model
plot_model_fixed(m, d,
                 gt = list(bA = pA, 
                           bS = boot::inv.logit(b_stick), 
                           sig_d = sig_d,
                           sig_theta = sig_theta))    
ggsave("../plots/sensiv_sim.pdf", width = 8, height = 2.8)
```

Compute posterior probability of a difference

```{r, fig.height=2.8}
 m %>% recover_types(d$found) %>%
    spread_draws(bA[block], bS[block], sigma_dis[block], sigma_dir[block]) %>%
    mutate(block = as_factor(block)) %>%
    ungroup() -> post
  
levels(post$block) <- cond_labels 

post %>% pivot_longer(c(bA, bS, sigma_dis, sigma_dir), names_to = "param") %>%
  pivot_wider(names_from = "block", values_from = "value") %>%
  mutate(diff = scarce-equal) -> post

post %>% group_by(param) %>%
  summarise(p_diff_gr0 = mean(diff>0)) %>%
  knitr::kable()

post %>% group_by(param) %>%
  median_hdci(diff, .width = 0.97) %>%
  knitr::kable(digits = 3)

post %>%
  ggplot(aes(diff)) + geom_density(fill = "grey") + 
  geom_vline(xintercept = 0, linetype = 2) + 
  facet_wrap(~param, scales="free", nrow = 1)
```
